\begin{thebibliography}{99}

\bibitem{lu2026attribution}
Lu, MingYu, Huang, Yushan, and Lee, Su-In.
\newblock An Attribution Framework for Multi-Agent LLMs.
\newblock \emph{ICLR 2026 AIWILD Workshop}, 2026.
\newblock OpenReview. \url{https://openreview.net/forum?id=esabw9linR}.

\bibitem{lu2026agents}
Lu, Mingyu, Huang, Yushan, Lin, Chris, and Lee, Su-In.
\newblock Agents that Matter: Optimizing Multi-Agent LLMs via Removal-Based Attribution.
\newblock arXiv:2605.27621, 2026.
\newblock \url{https://arxiv.org/abs/2605.27621}.

\bibitem{kim2026teambench}
Kim, Yubin, Park, Chanwoo, Kim, Taehan, Park, Eugene, Schmidgall, Samuel, Rahman, Salman, Park, Chunjong, Breazeal, Cynthia, Liu, Xin, Palangi, Hamid, Park, Hae Won, and McDuff, Daniel.
\newblock TeamBench: Evaluating Agent Coordination under Enforced Role Separation.
\newblock arXiv:2605.07073, 2026.
\newblock \url{https://arxiv.org/abs/2605.07073}.

\bibitem{zhu2025multiagentbench}
Zhu, Kunlun, Du, Hongyi, Hong, Zhaochen, Yang, Xiaocheng, Guo, Shuyi, Wang, Zhe, Wang, Zhenhailong, Qian, Cheng, Tang, Xiangru, Ji, Heng, and You, Jiaxuan.
\newblock MultiAgentBench: Evaluating the Collaboration and Competition of LLM Agents.
\newblock arXiv:2503.01935, 2025.
\newblock \url{https://arxiv.org/abs/2503.01935}.

\bibitem{hong2023metagpt}
Hong, Sirui, Zhuge, Mingchen, Chen, Jiaqi, Zheng, Xiawu, Cheng, Yuheng, Zhang, Ceyao, Wang, Jinlin, Wang, Zili, Yau, Steven Ka Shing, Lin, Zijuan, Zhou, Liyang, Ran, Chenyu, Xiao, Lingfeng, Wu, Chenglin, and Schmidhuber, J{\"u}rgen.
\newblock {MetaGPT}: Meta Programming for a Multi-Agent Collaborative Framework.
\newblock arXiv:2308.00352, 2023.
\newblock \url{https://arxiv.org/abs/2308.00352}.

\bibitem{qian2023chatdev}
Qian, Chen, Liu, Wei, Liu, Hongzhang, Chen, Nuo, Dang, Yufan, Li, Jiahao, Yang, Cheng, Chen, Weize, Su, Yusheng, Cong, Xin, Xu, Juyuan, Li, Dahai, Liu, Zhiyuan, and Sun, Maosong.
\newblock {ChatDev}: Communicative Agents for Software Development.
\newblock arXiv:2307.07924, 2023.
\newblock \url{https://arxiv.org/abs/2307.07924}.

\bibitem{islam2024mapcoder}
Islam, Md. Ashraful, Ali, Mohammed Eunus, and Parvez, Md Rizwan.
\newblock {MapCoder}: Multi-Agent Code Generation for Competitive Problem Solving.
\newblock arXiv:2405.11403, 2024.
\newblock \url{https://arxiv.org/abs/2405.11403}.

\bibitem{wu2023autogen}
Wu, Qingyun, Bansal, Gagan, Zhang, Jieyu, Wu, Yiran, Li, Beibin, Zhu, Erkang, Jiang, Li, Zhang, Xiaoyun, Zhang, Shaokun, Liu, Jiale, Awadallah, Ahmed Hassan, White, Ryen W., Burger, Doug, and Wang, Chi.
\newblock {AutoGen}: Enabling Next-Gen LLM Applications via Multi-Agent Conversation.
\newblock arXiv:2308.08155, 2023.
\newblock \url{https://arxiv.org/abs/2308.08155}.

\bibitem{li2023camel}
Li, Guohao, Hammoud, Hasan Abed Al Kader, Itani, Hani, Khizbullin, Dmitrii, and Ghanem, Bernard.
\newblock {CAMEL}: Communicative Agents for ``Mind'' Exploration of Large Language Model Society.
\newblock arXiv:2303.17760, 2023.
\newblock \url{https://arxiv.org/abs/2303.17760}.

\bibitem{chen2021evaluating}
Chen, Mark, Tworek, Jerry, Jun, Heewoo, Yuan, Qiming, Pinto, Henrique Pond{\'e} de Oliveira, Kaplan, Jared, Edwards, Harri, Burda, Yuri, Joseph, Nicholas, Brockman, Greg, Ray, Alex, Puri, Raul, Krueger, Gretchen, Petrov, Michael, Khlaaf, Heidy, Sastry, Girish, Mishkin, Pamela, Chan, Brooke, Gray, Scott, Ryder, Nick, Pavlov, Mikhail, Power, Alethea, Kaiser, Lukasz, Bavarian, Mohammad, Winter, Clemens, Tillet, Philippe, Such, Felipe Petroski, Cummings, Dave, Plappert, Matthias, Chantzis, Fotios, Barnes, Elizabeth, Herbert-Voss, Ariel, Guss, William Hebgen, Nichol, Alex, Paino, Alex, Tezak, Nikolas, Tang, Jie, Babuschkin, Igor, Balaji, Suchir, Jain, Shantanu, Saunders, William, Hesse, Christopher, Carr, Andrew N., Leike, Jan, Achiam, Josh, Misra, Vedant, Morikawa, Evan, Radford, Alec, Knight, Matthew, Brundage, Miles, Murati, Mira, Mayer, Katie, Welinder, Peter, McGrew, Bob, Amodei, Dario, McCandlish, Sam, Sutskever, Ilya, and Zaremba, Wojciech.
\newblock Evaluating Large Language Models Trained on Code.
\newblock arXiv:2107.03374, 2021.
\newblock \url{https://arxiv.org/abs/2107.03374}.

\bibitem{austin2021program}
Austin, Jacob, Odena, Augustus, Nye, Maxwell, Bosma, Maarten, Michalewski, Henryk, Dohan, David, Jiang, Ellen, Cai, Carrie, Terry, Michael, Le, Quoc, and Sutton, Charles.
\newblock Program Synthesis with Large Language Models.
\newblock arXiv:2108.07732, 2021.
\newblock \url{https://arxiv.org/abs/2108.07732}.

\bibitem{jimenez2023swebench}
Jimenez, Carlos E., Yang, John, Wettig, Alexander, Yao, Shunyu, Pei, Kexin, Press, Ofir, and Narasimhan, Karthik.
\newblock {SWE-bench}: Can Language Models Resolve Real-World GitHub Issues?
\newblock arXiv:2310.06770, 2023.
\newblock \url{https://arxiv.org/abs/2310.06770}.

\bibitem{shapley1953value}
Shapley, Lloyd S.
\newblock A Value for n-Person Games.
\newblock In Kuhn, H. W. and Tucker, A. W., editors, \emph{Contributions to the Theory of Games II}, pages 307--317. Princeton University Press, Princeton, NJ, 1953.

\bibitem{banzhaf1965weighted}
Banzhaf, John F.
\newblock Weighted Voting Doesn't Work: A Mathematical Analysis.
\newblock \emph{Rutgers Law Review}, 19:317--343, 1965.

\bibitem{myerson1977graphs}
Myerson, Roger B.
\newblock Graphs and Cooperation in Games.
\newblock \emph{Mathematics of Operations Research}, 2(3):225--229, 1977.

\bibitem{owen1977values}
Owen, Guillermo.
\newblock Values of Games with A Priori Unions.
\newblock In Henn, Rudolf and Moeschlin, Otto, editors, \emph{Mathematical Economics and Game Theory: Essays in Honor of Oskar Morgenstern}, pages 76--88. Springer, Berlin, 1977.

\bibitem{wang2024survey_agents}
Wang, Lei, Ma, Chen, Feng, Xueyang, Zhang, Zeyu, Yang, Hao, Zhang, Jingsen, Chen, Zhiyuan, Tang, Jiakai, Chen, Xu, Lin, Yankai, Zhao, Wayne Xin, Wei, Zhe, and Wen, Ji-Rong.
\newblock A Survey on Large Language Model Based Autonomous Agents.
\newblock arXiv:2308.11432, 2024.
\newblock \url{https://arxiv.org/abs/2308.11432}.

\bibitem{guo2024llm_ma_survey}
Guo, Taicheng, Chen, Xiuying, Wang, Yaqi, Chang, Ruidi, Pei, Shichao, Chawla, Nitesh V., Wiest, Olaf, and Zhang, Xiangliang.
\newblock Large Language Model Based Multi-Agents: A Survey of Progress and Challenges.
\newblock In \emph{Proceedings of the Thirty-Third International Joint Conference on Artificial Intelligence}, 2024.
\newblock \url{https://www.ijcai.org/proceedings/2024/890}.

\bibitem{chen2024llm_mas_survey}
Chen, Shuaihang, Liu, Yuanxing, Han, Wei, Zhang, Weinan, and Liu, Ting.
\newblock A Survey on LLM-Based Multi-Agent System: Recent Advances and New Frontiers in Application.
\newblock arXiv:2412.17481, 2024.
\newblock \url{https://arxiv.org/abs/2412.17481}.

\bibitem{chen2023agentverse}
Chen, Weize, Su, Yusheng, Zuo, Jingwei, Yang, Cheng, Yuan, Chenfei, Chan, Chi-Min, Yu, Heyang, Lu, Yaxi, Hung, Yi-Hsin, Qian, Chen, Qin, Yujia, Cong, Xin, Xie, Ruobing, Liu, Zhiyuan, Sun, Maosong, and Zhou, Jie.
\newblock {AgentVerse}: Facilitating Multi-Agent Collaboration and Exploring Emergent Behaviors.
\newblock arXiv:2308.10848, 2023.
\newblock \url{https://arxiv.org/abs/2308.10848}.

\bibitem{liu2023agentbench}
Liu, Xiao, Yu, Hao, Zhang, Hanchen, Xu, Yifan, Lei, Xuanyu, Lai, Hanyu, Gu, Yu, Ding, Hangliang, Men, Kaiwen, Yang, Kejuan, Zhang, Shudan, Deng, Xiang, Zeng, Aohan, Du, Zhengxiao, Zhang, Chenhui, Shen, Sheng, Zhang, Tianjun, Su, Yu, Sun, Huan, Huang, Minlie, Dong, Yuxiao, and Tang, Jie.
\newblock {AgentBench}: Evaluating LLMs as Agents.
\newblock In \emph{The Twelfth International Conference on Learning Representations}, 2024.
\newblock \url{https://openreview.net/forum?id=zAdUB0aCTQ}.

\bibitem{ma2024agentboard}
Ma, Chang, Zhang, Junlei, Zhu, Zhihao, Yang, Cheng, Yang, Yujiu, Jin, Yaohui, Lan, Zhenzhong, Kong, Lingpeng, and He, Junxian.
\newblock {AgentBoard}: An Analytical Evaluation Board of Multi-Turn LLM Agents.
\newblock arXiv:2401.13178, 2024.
\newblock \url{https://arxiv.org/abs/2401.13178}.

\bibitem{wang2023mint}
Wang, Xingyao, Wang, Zihan, Liu, Jiateng, Chen, Yangyi, Yuan, Lifan, Peng, Hao, and Ji, Heng.
\newblock {MINT}: Evaluating LLMs in Multi-Turn Interaction with Tools and Language Feedback.
\newblock In \emph{The Twelfth International Conference on Learning Representations}, 2024.
\newblock \url{https://openreview.net/forum?id=jp3gWrMuIZ}.

\bibitem{agashe2025llmcoordination}
Agashe, Saaket, Fan, Yue, Reyna, Anthony, and Wang, Xin Eric.
\newblock {LLM-Coordination}: Evaluating and Analyzing Multi-Agent Coordination Abilities in Large Language Models.
\newblock In \emph{Findings of the Association for Computational Linguistics: NAACL 2025}, pages 8088--8116, 2025.
\newblock \url{https://aclanthology.org/2025.findings-naacl.448/}.

\bibitem{gong2023mindagent}
Gong, Ran, Huang, Qiuyuan, Ma, Xiaojian, Vo, Hoi, Durante, Zane, Noda, Yusuke, Zheng, Zilong, Zhu, Song-Chun, Terzopoulos, Demetri, Fei-Fei, Li, and Gao, Jianfeng.
\newblock {MindAgent}: Emergent Gaming Interaction.
\newblock In \emph{Findings of the Association for Computational Linguistics: NAACL 2024}, 2024.
\newblock \url{https://aclanthology.org/2024.findings-naacl.200/}.

\bibitem{zhou2024sotopia}
Zhou, Xuhui, Zhu, Hao, Mathur, Leena, Zhang, Ruohong, Yu, Haofei, Qi, Zhengyang, Morency, Louis-Philippe, Bisk, Yonatan, Fried, Daniel, Neubig, Graham, and Sap, Maarten.
\newblock {SOTOPIA}: Interactive Evaluation for Social Intelligence in Language Agents.
\newblock In \emph{The Twelfth International Conference on Learning Representations}, 2024.
\newblock \url{https://openreview.net/forum?id=mM7VurbA4r}.

\bibitem{mahmud2025collab}
Mahmud, Saaduddin, Bagdasarian, Eugene, and Zilberstein, Shlomo.
\newblock {CoLLAB}: A Framework for Designing Scalable Benchmarks for Coordinating LLM Agents.
\newblock \emph{SEA @ NeurIPS 2025}, 2025.
\newblock \url{https://openreview.net/forum?id=372FjQy1cF}.

\bibitem{zou2026calbench}
Zou, Chelsea, Yao, Yiheng, She, Selena, Goodman, Noah D., and Hawkins, Robert D.
\newblock {CalBench}: Evaluating Coordination--Privacy Trade-offs in Multi-Agent LLMs.
\newblock arXiv:2605.09823, 2026.
\newblock \url{https://arxiv.org/abs/2605.09823}.

\bibitem{mazumder2026agentcollabbench}
Mazumder, Aritra, Dipta, Shubhashis Roy, Lia, Nusrat Jahan, Khan, Tanzila, Hossain, Kainat Raisa, Shri, Nehaa, Debsarkar, Shubhrangshu, Tasnim, Humayra, Shawon, Gour Gupal Talukder, Mitra, Debjoty, Rani, Sumaiya Ahmed, Anik, Al Jami Islam, and Khan, Al Nafeu.
\newblock {AgentCollabBench}: Diagnosing When Good Agents Make Bad Collaborators.
\newblock arXiv:2605.08647, 2026.
\newblock \url{https://arxiv.org/abs/2605.08647}.

\bibitem{lundberg2017unified}
Lundberg, Scott M. and Lee, Su-In.
\newblock A Unified Approach to Interpreting Model Predictions.
\newblock In \emph{Advances in Neural Information Processing Systems}, volume 30, 2017.
\newblock \url{https://proceedings.neurips.cc/paper_files/paper/2017/hash/8a20a8621978632d76c43dfd28b67767-Abstract.html}.

\bibitem{ghorbani2019data}
Ghorbani, Amirata and Zou, James.
\newblock Data Shapley: Equitable Valuation of Data for Machine Learning.
\newblock In \emph{Proceedings of the 36th International Conference on Machine Learning}, 2019.
\newblock \url{https://proceedings.mlr.press/v97/ghorbani19c.html}.

\bibitem{yang2025capabench}
Yang, Yingxuan, Huang, Bo, Qi, Siyuan, Feng, Chao, Hu, Haoyi, Zhu, Yuxuan, Hu, Jinbo, Zhao, Haoran, He, Ziyi, Liu, Xiao, Wang, Zongyu, Qiu, Lin, Cao, Xuezhi, Cai, Xunliang, Yu, Yong, and Zhang, Weinan.
\newblock Who's the MVP? A Game-Theoretic Evaluation Benchmark for Modular Attribution in LLM Agents.
\newblock arXiv:2502.00510, 2025.
\newblock \url{https://arxiv.org/abs/2502.00510}.

\bibitem{xia2026hivemind}
Xia, Yihan, Wang, Taotao, Zhang, Shengli, Weng, Zhangyuhua, Cao, Bin, and Liew, Soung Chang.
\newblock {HiveMind}: Contribution-Guided Online Prompt Optimization of LLM Multi-Agent Systems.
\newblock In \emph{Proceedings of the AAAI Conference on Artificial Intelligence}, volume 40, pages 34411--34419, 2026.
\newblock \url{https://ojs.aaai.org/index.php/AAAI/article/view/40222}.

\bibitem{freeman1977set}
Freeman, Linton C.
\newblock A Set of Measures of Centrality Based on Betweenness.
\newblock \emph{Sociometry}, 40(1):35--41, 1977.

\bibitem{bonacich1987power}
Bonacich, Phillip.
\newblock Power and Centrality: A Family of Measures.
\newblock \emph{American Journal of Sociology}, 92(5):1170--1182, 1987.

\bibitem{page1999pagerank}
Page, Lawrence, Brin, Sergey, Motwani, Rajeev, and Winograd, Terry.
\newblock The PageRank Citation Ranking: Bringing Order to the Web.
\newblock Technical Report 1999-66, Stanford InfoLab, 1999.

\bibitem{newman2010networks}
Newman, Mark E. J.
\newblock \emph{Networks: An Introduction}.
\newblock Oxford University Press, 2010.

\bibitem{yan2025communication_survey}
Yan, Bingyu, Zhang, Xiaoming, Zhang, Litian, Zhang, Lian, Zhou, Ziyi, Miao, Dezhuang, and Li, Chaozhuo.
\newblock Beyond Self-Talk: A Communication-Centric Survey of LLM-Based Multi-Agent Systems.
\newblock arXiv:2502.14321, 2025.
\newblock \url{https://arxiv.org/abs/2502.14321}.

\bibitem{wolpert2001optimal}
Wolpert, David H. and Tumer, Kagan.
\newblock Optimal Payoff Functions for Members of Collectives.
\newblock \emph{Advances in Complex Systems}, 4(2--3):265--279, 2001.

\bibitem{sunehag2018value}
Sunehag, Peter, Lever, Guy, Gruslys, Audrunas, Czarnecki, Wojciech M., Zambaldi, Vinicius, Jaderberg, Max, Lanctot, Marc, Sonnerat, Nicolas, Leibo, Joel Z., Tuyls, Karl, and Graepel, Thore.
\newblock Value-Decomposition Networks For Cooperative Multi-Agent Learning.
\newblock arXiv:1706.05296, 2017.
\newblock \url{https://arxiv.org/abs/1706.05296}.

\bibitem{rashid2018qmix}
Rashid, Tabish, Samvelyan, Mikayel, De Witt, Christian Schroeder, Farquhar, Gregory, Foerster, Jakob, and Whiteson, Shimon.
\newblock {QMIX}: Monotonic Value Function Factorisation for Deep Multi-Agent Reinforcement Learning.
\newblock In \emph{Proceedings of the 35th International Conference on Machine Learning}, 2018.
\newblock \url{https://proceedings.mlr.press/v80/rashid18a.html}.

\bibitem{foerster2018coma}
Foerster, Jakob N., Farquhar, Gregory, Afouras, Triantafyllos, Nardelli, Nantas, and Whiteson, Shimon.
\newblock Counterfactual Multi-Agent Policy Gradients.
\newblock In \emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 2018.
\newblock \url{https://ojs.aaai.org/index.php/AAAI/article/view/11794}.

\end{thebibliography}
